Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise

### 2016-09-05 main.tex
WIP on the discussion

The significant impact of the machine-like \vs human-like conditions on the
answers to the question \emph{Were the tasks more ``a robot kind of task'' or
``a human kind of task''?} shows that our manipulation was effective: framing
the interaction situation to induce a machine-like or a human-like task context
was successful.

situation priming the participants with , and that a machine-like cognitive
context was indeed perceived to elicit a ``robot-like'' situation, while a
human-like
cognitive priming was perceived as a ``human-like'' situation. This supports our
first hypothesis \h{1}: even indirect hints at the cognitive capabilities of a robot are
sufficient to elicit significantly increased attribution of human-likeness.

@@

\subsection{Design of the Stimuli and Applicability of the Method to Real World
Scenarios}
\label{stimuli_design}

>>>>

The significant impact of the machine-like \vs human-like conditions on the
answers to the question \emph{Were the tasks more ``a robot kind of task'' or
``a human kind of task''?} shows that our manipulation was effective: framing
the interaction situation to induce a machine-like or a human-like task context
was successful. By further showing that the conditions also impact the
reported tendency to attribute anthropomorphic traits to robots in general (as assessed by
the Godspeed questionnaire), we conclude that our manipulation of the commands
given to the robot effectively influenced how anthropomorphic the participants
perceived the robot.

We interpret this result as the participants building in each condition a different set of
expected cognitive skills for the robot: when a participant hears the robot
being instructed ``Pick up your favourite toy'', she implicitly (and likely,
unconsciously) supposes that the robot has the cognitive capabilities required
to \emph{prefer} one toy to another one, which would typically implies that the robot
understand the affective dimensions of the different toys. By performing this
reasoning, we believe the human (likely unconsciously) does attribute cognitive and emotional
traits to the robot that are akin to humans, and as a result, anthropomorphise
more the robot.

@@

\paragraph{Design of the Stimuli and Applicability of the Method to Real World
Scenarios}
\label{stimuli_design}
